Scan-Centric, Frequency-Based Method for Characterizing Peaks from Direct Injection Fourier transform Mass Spectrometry Experiments

### 2022-04-09 doc/peakcharacterization_manuscript.Rmd
fixing styles

::: {custom-style="MDPI_3.9_text"}
To associate the XCalibur and MSnbase peaks with the scan-centric peaks, a 4 ppm (2ppm low and high) window is calculated for the scan-centric centroid, and if any peaks are found within the window, the one with the smallest m/z difference is kept as the matching peak to the scan-centric one under consideration.
:::

@@

::: {custom-style="MDPI_2.1_heading2"}
### Software Used
:::

Thermo-Fisher XCalibur was used to export peak lists from all samples used.
SMIRFE v 1.0 [@mitchellSmallMoleculeIsotope2019] running under Python 3.8 [@vanrossumPython3] was used for assignments.
Lipid classifications were generated by LipidClassifier v 1.0 [@mitchellDerivingLipidClassification2020].
All other calculations were performed in R v 4.1.0 [@rcoreteam_rlanguage_2020].
The targets package v 0.10.0 was used to control processing and aggregation of results [@landauTargetsPackageDynamic2021], and renv v 0.15.3 [@usheyRenvProjectEnvironments2022] to create a reproducible R package environment.
Plots were generated using ggplot2 v 3.3.5 [@wickhamGgplot2ElegantGraphics2016], patchwork v 1.1.1 [@pedersenPatchworkComposerPlots2020], ComplexHeatmap v 2.10.0 [@guComplexHeatmapsReveal2016a], ggridges v 0.5.3 [@wilkeGgridgesRidgelinePlots2021], and ggforce v 0.3.3 [@pedersenGgforceAcceleratingGgplot22021].
MSnbase v 2.20.4 [@gattoMSnbaseEfficientElegant2020; @gattoMSnbaseBioconductorPackage2012] provided facilities for reading in scan-level data, merging scans and calculating centroided peaks.
ICI-Kt correlation values among lipid samples were calculated using ICIKendallTau v 0.1.16 [@flightInformationContentInformedKendalltauCorrelation2022].
Outlier lipid samples were determined using visualizationQualityControl v 0.4.7 [@flightVisualizationQualityControlDevelopmentVisualization2021].
Specific data manipulation facilities were provided by dplyr v 1.0.8 [@wickhamDplyrGrammarData2022], tidyr v 1.2.0 [@wickhamTidyrTidyMessy2022], furrr v 0.2.3 [@vaughanFurrrApplyMapping2021a], 
This manuscript was generated from rmarkdown v 2.11 [@allaireRmarkdownDynamicDocuments2021; @xieMarkdownDefinitiveGuide2018; xieMarkdownCookbook2020].

::: {custom-style="MDPI_2.1_heading2"}
### Availability
:::

The code used in the reporting of results is available on GitHub at https://github.com/MoseleyBioinformaticsLab/manuscript.peakCharacterization, and archived on Zenodo [ref].
The scan-centric peak-characterization is packaged as an R package at https://github.com/MoseleyBioinformaticsLab/FTMS.peakCharacterization, and the specific version used in this work is archived on Zenodo [ref].

>>>>

::: {custom-style="MDPI_3.1_text"}
To associate the XCalibur and MSnbase peaks with the scan-centric peaks, a 4 ppm (2ppm low and high) window is calculated for the scan-centric centroid, and if any peaks are found within the window, the one with the smallest m/z difference is kept as the matching peak to the scan-centric one under consideration.
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Software Used
:::

::: {custom-style="MDPI_3.1_text"}
Thermo-Fisher XCalibur was used to export peak lists from all samples used.
SMIRFE v 1.0 [@mitchellSmallMoleculeIsotope2019] running under Python 3.8 [@vanrossumPython3] was used for assignments.
Lipid classifications were generated by LipidClassifier v 1.0 [@mitchellDerivingLipidClassification2020].
All other calculations were performed in R v 4.1.0 [@rcoreteam_rlanguage_2020].
The targets package v 0.10.0 was used to control processing and aggregation of results [@landauTargetsPackageDynamic2021], and renv v 0.15.3 [@usheyRenvProjectEnvironments2022] to create a reproducible R package environment.
Plots were generated using ggplot2 v 3.3.5 [@wickhamGgplot2ElegantGraphics2016], patchwork v 1.1.1 [@pedersenPatchworkComposerPlots2020], ComplexHeatmap v 2.10.0 [@guComplexHeatmapsReveal2016a], ggridges v 0.5.3 [@wilkeGgridgesRidgelinePlots2021], and ggforce v 0.3.3 [@pedersenGgforceAcceleratingGgplot22021].
MSnbase v 2.20.4 [@gattoMSnbaseEfficientElegant2020; @gattoMSnbaseBioconductorPackage2012] provided facilities for reading in scan-level data, merging scans and calculating centroided peaks.
ICI-Kt correlation values among lipid samples were calculated using ICIKendallTau v 0.1.16 [@flightInformationContentInformedKendalltauCorrelation2022].
Outlier lipid samples were determined using visualizationQualityControl v 0.4.7 [@flightVisualizationQualityControlDevelopmentVisualization2021].
Specific data manipulation facilities were provided by dplyr v 1.0.8 [@wickhamDplyrGrammarData2022], tidyr v 1.2.0 [@wickhamTidyrTidyMessy2022], furrr v 0.2.3 [@vaughanFurrrApplyMapping2021a], 
This manuscript was generated from rmarkdown v 2.11 [@allaireRmarkdownDynamicDocuments2021; @xieMarkdownDefinitiveGuide2018; xieMarkdownCookbook2020].
:::

::: {custom-style="MDPI_2.2_heading2"}
### Availability
:::

::: {custom-style="MDPI_3.1_text"}
The code used in the reporting of results is available on GitHub at https://github.com/MoseleyBioinformaticsLab/manuscript.peakCharacterization, and archived on Zenodo [ref].
The scan-centric peak-characterization is packaged as an R package at https://github.com/MoseleyBioinformaticsLab/FTMS.peakCharacterization, and the specific version used in this work is archived on Zenodo [ref].
:::
